Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
editing...

\paragraph{Amplifying groups for boundary cases.} Recall in the
three-level policy, the medium gap case (Lemma \ref{3levelmedium})
corresponds to the case where the gap $\Delta$ is between
$\Omega\left({{1}/{T_1}}\right)$ and
$O\left(\sqrt{{\log(T)}/{T_1}}\right)$. This is a boundary case since
$\Delta$ is neither large enough to conclude that with high
probability agents in both the second level and the third level all
pull the best arm, nor small enough to conclude that both arms are
explored enough times in the second level (due to
anti-concentration). In this case, we need to ensure that agents in
the third level can eliminate the inferior arm. This issue is easily
resolved in the three-level policy since the agents in the third level
observe the history of the entire first level, which provides
sufficiently accurate reward estimates for both arms.

@@

In the $L$-level policy, such boundary case occurs for each
intermediate level $l\in \{\}$. Moreover, the worry mentioned above does not get
naturally resolved as in some of these boundary cases, the ratios
between the upper and lower bounds of the gap rise from
$\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$. The reason for such
rise is that, except the first level, we don't have good enough
guarantee of the number of pulls of each arm. For example, in Figure
\ref{fig:llevel-connecting}, when we talk about having enough arm $a$
pulls in the history observed by agents in $G_{l,1,1}$, it could be
that only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it
also could be that most agents in groups
$G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm
$a$. Therefore our estimate of the number of arm $a$ pulls can be off
by an $\NG=\Theta(\log(T))$ multiplicative factor. This finally makes
the boundary cases harder to deal with.

>>>>

\paragraph{Amplifying groups for boundary cases.} Recall in the
three-level policy, the medium gap case (Lemma \ref{3levelmedium})
corresponds to the case where the gap $\Delta$ is between
$\Omega\left(\sqrt{{1}/{T_1}}\right)$ and
$O\left(\sqrt{{\log(T)}/{T_1}}\right)$. This is a boundary case since
$\Delta$ is neither large enough to conclude that with high
probability agents in both the second level and the third level all
pull the best arm, nor small enough to conclude that both arms are
explored enough times in the second level (due to
anti-concentration). In this case, we need to ensure that agents in
the third level can eliminate the inferior arm. This issue is easily
resolved in the three-level policy since the agents in the third level
observe the history of the entire first level, which provides
sufficiently accurate reward estimates for both arms.

@@

In the $L$-level policy, such boundary case occurs for each
intermediate level $l\in \{2, \ldots, l-1\}$, but issue mentioned
above does not get naturally resolved as in some of these boundary
cases---the ratios between the upper and lower bounds of $\Delta$ rise
from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$, and it would
require more observations from level $(l-2)$ to distinguish two arms
at level $l$. The reason for this larger disparity is that, except the
first level, we can no longer guarantee sufficient number of pulls of
each arm. For example, in as shown in Figure
\ref{fig:llevel-connecting}, when we talk about having enough arm $a$
pulls in the history observed by agents in $G_{l,1,1}$, it could be
that only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it
also could be that most agents in groups
$G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm
$a$. Therefore our estimate of the number of arm $a$ pulls can be off
by an $\NG=\Theta(\log(T))$ multiplicative factor. This finally makes
the boundary cases harder to deal with.
